Title

### 2021-02-15 Thesis/article.tex
thesis mail to theo about sol-gel process

>>>>

Making of the solution for the sol-gel process:
For a single concentrated solution 0.05 ml of Zr(IV)Propoxide are added while stirring to 4.95 ml of Buthan-1-ol and stirred for 15 minutes. 
0.013 ml (or one molar equvilent of Zr) of Acetylacetone is added to the stirring solution. After another 15 minutes 1 ml of Aceteicacid is added and stirred for 30 minutes to stabilize the solution up to 24h.

The concentration can be increased up to 5 times being stable for a minimum of 4 hours. The sol-gel process produces am homogeneous transparent crystalline zirconia oxide layer. homogeneity can be mainly controlled via blade velocity and temperature and layers can be stacked.
